biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-11-22 paper/PaperCEUS/PaperCEUS.Rmd
remember things

Please make sure that your manuscript follows the guidelines in the 
Guide for Authors of the relevant journal. It is not necessary to 
typeset your manuscript in exactly the same way as an article, 
unless you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see   <https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions>

<!-- TODO: -->
<!-- check if HEAT estimates remain the same (the tool is not working atm) -->
<!-- should we ignore the social benefits component? and only estimate and add the environmental ones? or estimate the car to tp transfer Social benefits? maybe to the next paper? -->

@@

To achieve the cycling targets set by the Portuguese national cycling strategy for 2025 and 2030 (4% and 10%, respectively) [@ENMAC], the Lisbon's Metropolitan Department of Transport introduced *biclaR*[^1], a decision support tool that facilitates the design and development of a metropolitan cycling network [@felix2023].

@@

>>>>

<!-- TODO: -->
<!-- check if HEAT estimates remain the same (the tool is not working atm) -->
<!-- should we ignore the social benefits component? and only estimate and add the environmental ones? or estimate the car to PT transfer Social benefits? maybe to the next paper? -->
<!-- should we keep both direct and safe routing is is it just noise? -->

@@

To achieve the cycling targets set by the Portuguese national cycling strategy for 2025 and 2030 (4% and 10%, respectively) [@ENMAC], the Lisbon's Metropolitan Department of Transport introduced *biclaR*[^1], a decision support tool that facilitates the planning, design, and development of a metropolitan cycling network [@felix2023].

@@

There are also social benefits form shifting car trips to PT, nevertheless those were not estimated in this research.
One of the main socioenvironmetal benefits, valued after monetization, comes from the increase in physical activity [@Felix2023ES].
The literature shows that the Metabolic Equivalent Tasks (MET) for "riding in a bus or a train" is 1.3 plus the "walking for transportation" is 3.5, while driving a car is 2.5. see https://golf.procon.org/met-values-for-800-activities/
The difference is not that much between them.
Future works should also encompass the estimation of the social impacts for the PT leg of the journey, shifting from car.

### 2023-11-22 paper/PaperCEUS/PaperCEUS.tex
remember things

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

@@

To achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively) (Presidência do
Conselho de Ministros, 2019), the Lisbon's Metropolitan Department of
Transport introduced \emph{biclaR}\footnote{See
  \href{https://biclar.tmlmobilidade.pt/}{biclar.tmlmobilidade.pt}.}, a
decision support tool that facilitates the design and development of a
metropolitan cycling network (Félix et al., 2022).

@@

@@

>>>>

@@

To achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively) (Presidência do
Conselho de Ministros, 2019), the Lisbon's Metropolitan Department of
Transport introduced \emph{biclaR}\footnote{See
  \href{https://biclar.tmlmobilidade.pt/}{biclar.tmlmobilidade.pt}.}, a
decision support tool that facilitates the planning, design, and
development of a metropolitan cycling network (Félix et al., 2022).

@@

There are also social benefits form shifting car trips to PT,
nevertheless those were not estimated in this research. One of the main
socioenvironmetal benefits, valued after monetization, comes from the
increase in physical activity (Félix et al., 2023). The literature shows
that the Metabolic Equivalent Tasks (MET) for ``riding in a bus or a
train'' is 1.3 plus the ``walking for transportation'' is 3.5, while
driving a car is 2.5. see
https://golf.procon.org/met-values-for-800-activities/ The difference is
not that much between them. Future works should also encompass the
estimation of the social impacts for the PT leg of the journey, shifting
from car.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Felix2023ES}{}}%
Félix, R., Orozco-Fontalvo, M., \& Moura, F. (2023). Socio-economic
assessment of shared e-scooters: Do the benefits overcome the
externalities? \emph{Transportation Research Part D: Transport and
Environment}, \emph{118}, 103714.
https://doi.org/\url{https://doi.org/10.1016/j.trd.2023.103714}
